\documentclass[a4paper,titlepage]{article}
\usepackage[final]{pdfpages}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{inconsolata}
\usepackage{url}
\usepackage{color}
\usepackage{setspace}


\hypersetup{
    bookmarks=true,         % show bookmarks bar?
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black
}


\title{Test Report\\v0.2 Beta}
\author{Andreas Berggren\\
        Gustav Freij\\
        Christoffer Karlsson}
\date{\today}

\begin{document}

\maketitle

% Table of contents
\pagenumbering{roman}
\tableofcontents
\newpage

% 
\setcounter{page}{1}
\pagenumbering{arabic}


\section{Introduction}
\subsection{Purpose of application}
Have a ball move using the accelerometer and interact with generated walls.

\subsection{General characteristics of application}
Using the accelerometer the ball will be guided over the playing field.

\newpage
\section{Test enviroment}
%Vilka förberedelser behöver göras innan man kan testa
%** Var finns koden eller .apk?
%** Hur installeras denna?
%** Behöver man tömma eller skapa en databas?
%** Behövs internetuppkoppling (kanske ett spciellt nätverk)?
The compiled application, .apk, can be downloaded from \url{https://github.com/ChristofferKarlsson/Labyrinth/downloads}. The downloadable application is
compiled from the source code on GIT with the tag \texttt{v0.2\_beta}.
%No other preparations are required before installing and using the application.

\subsection{Hardware enviroment}
%(what computers/devices was/wered used?)
%Använder ni emulatorn eller riktig telefon vid dessa?
The devices used to test the application are the Samsung Galaxy S and Samsung
Galaxy S2.

\subsection{Software environment}
%(what software (incl version) was used?)
\subsubsection{Softwares}
The software environments used to test the application are Android 2.3.3 and
Android 4.0.3.
\subsubsection{Software settings}
No specific settings are needed.

\newpage
\section{System information}
\subsection{System version}
%(what version of your software is tested in this document)
Version 0.2 Beta.

\newpage
\section{Known bugs and limitations}
%(list all bugs you knew of before the test)
\subsubsection{Bugs}
\begin{itemize}
  \item The ball is thought upon as a rectangle, meaning it only has four reference points, and therefore all of its edges are not immediately discovered by the collision handler.
  \item Sometimes the ball is stopped slightly within a wall which causes the graphics to look out of place.
\end{itemize}

\subsubsection{Limitations}
No limitations.

\newpage
\section{Test specifcation}
%(list the name and version of the test documentation (doc with test cases))
The test cases can be found in the document \texttt{test\_cases.pdf}.

\newpage
\section{Automatic test}
\subsection{Code coverage}
%Använder ni kodtäckningsverktyg, vilken grad av kodtäckning siktar
%ni på? – motivera
No code coverage is used.
\subsection{Nightly builds}
%Om ni gör detta, beskriv hur, var, när detta görs
No nightly builds are being done, yet.
\subsection{Unit test}
%Vilka unit test-programvaror använder ni

%Finns det saker som ni inte kan testa via unit tests – dokumentera
%och motivera detta
No unit tests have been developed, yet.

\newpage
\section{Test report}
%Vad testas?  Är det senaste versionen i GIT (inte bra!), eller en upptagged
%release (bra!).
The test is done on the GIT version tagged as \texttt{v0.2\_beta}.\\
%(present a table with Test id, Result, Comment)
%(use comment to say what bug the test resulted in or that the test could not be performed since the requirement is not yet implemented)

\begin{tabularx}{\textwidth}{XXX}
	Test id & Result    & Comment\\
\hline\\
	1.1     & Passed      & -\\
	1.2     & Passed      & -\\
	1.3     & Passed      & -\newline\\
	2.1     & Passed      & -\\
	2.2     & -           & Not implemented\\
	2.3     & Passed      & -\\
	2.4     & Passed      & -\\
	2.5     & Passed      & Shaped like an 'L'\newline\\
	3.1     & -           & Not implemented\\
	3.2     & Passed      & -\newline\\
	4.1     & Passed      & -\\
	4.2     & Passed      & -\\
	4.5     & Not passed  & Not yet implemented\\
	4.6     & Passed      & -\newline\\
	5.1     & Passed      & -\\
	5.2     & Passed      & -\\
	5.5     & Passed      & -\\
\end{tabularx}
\end{document}
